### 2024-01-17 documentation/thesis/thesis_document.tex
more thesis
some additions to evaluation

\begin{lstlisting}[language=Python, caption={User implemented custom find most similar readings algorithm}, label=lst:custom_find_similar_values_algorithm]
@staticmethod
def FindSimilarValuesAlgorithm(_readings: [MRPReading.MRPReading], IP_return_count: int = -1) -> [MRPReading.MRPReading]:
  import heapq
  import math
  heap = []
  # SET RESULT VALUE COUNT
  IP_return_count = max([int(IP_return_count),len(_readings)])
  if IP_return_count < 0:
      IP_return_count = len(_readings) / 5
  # CALCULATE TARGET VALUE: CENTER OF GRAVITY MAGNITUDE FOR ALL READINGS
  target_value = 0.0
  for idx, r in enumerate(_readings):
      cog_vecotr = MRPAnalysis.MRPAnalysis.calculate_center_of_gravity(r)
      # COMPUTE LENGTH OF VECTOR
      cog:float = math.sqrt(cog[0]**2 + cog[1]**2 cog[2]**2)
      target_value = target_value + cog
  target_value = target_value / len(_readings)
  # PUSH READINGS TO HEAP
  for value in _readings:
      # USE DIFF AS PRIORITY VALUE IN MIN-HEAP
      diff = abs(value - target_value)
      heapq.heappush(heap, (diff, value))
  # RETURN X BEST ITEMS FROM HEAP
  similar_values = [item[1] for item in heapq.nsmallest(IP_return_count, heap)]
  # CLEAN UP USED LIBRARIES AND RETURN RESULT
  del heapq
  del math
  return similar_values
\end{lstlisting}

@@

@@

On the right-hand side
\ref{MRP_evaluation_result_after_execution_of_the _user_defined_pipeline,_using_find_similar_values_algorithm.png},
the measured values are plotted as a result of the filter algorithm. As
the \passthrough{\lstinline!IP\_return\_count!} parameter was set to
four, only the four most similar measurements were exported here. It can
be seen from the plotted \passthrough{\lstinline!CoG [uT]!} deviation
values, that these are closest to an ideal Magnet with a
\passthrough{\lstinline!CoG!} value of 0uT. This ideal value was
calculated with the function
\passthrough{\lstinline!MRP.MRPSimulation.generate\_simulated\_reading!},
with the same measurement parameters (magnet type, dimensions, sensor
distance) as they correspond to the mechanical structure of the used
hardware sensor \ref{d-fullsphere}. The filter algorithm implemented by
the user was thus successfully executed using the user-programmable
pipeline. The calculation result was successfully verified using raw
measurement data and the final result of the algorithm.

>>>>

\begin{lstlisting}[language=Python, caption={User implemented custom find most similar readings algorithm}, label=lst:custom_find_similar_values_algorithm]
@staticmethod
def FindSimilarValuesAlgorithm(_readings: [MRPReading.MRPReading], IP_return_count: int = -1) -> [MRPReading.MRPReading]:
  import heapq
  import math
  heap = []
  # SET RESULT VALUE COUNT
  IP_return_count = max([int(IP_return_count),len(_readings)])
  if IP_return_count < 0:
      IP_return_count = len(_readings) / 5
  # CALCULATE TARGET VALUE: CENTER OF GRAVITY MAGNITUDE FOR ALL READINGS
  target_value = 0.0
  for idx, r in enumerate(_readings):
      cog = MRPAnalysis.MRPAnalysis.calculate_center_of_gravity(r)
      # COMPUTE LENGTH OF VECTOR
      cog_value: float = math.sqrt(cog[0]**2 + cog[1]**2 cog[2]**2)
      target_value = target_value + cog
  target_value = target_value / len(_readings)
  # PUSH READINGS TO HEAP
  for value in _readings:
      # USE DIFF AS PRIORITY VALUE IN MIN-HEAP
      cog = MRPAnalysis.MRPAnalysis.calculate_center_of_gravity(value)
      cog_value: float = math.sqrt(cog[0]**2 + cog[1]**2 cog[2]**2)
      diff = abs(cog_value - target_value)
      heapq.heappush(heap, (diff, cog_value))
  # RETURN X BEST ITEMS FROM HEAP
  similar_values = [item[1] for item in heapq.nsmallest(IP_return_count, heap)]
  # CLEAN UP USED LIBRARIES AND RETURN RESULT
  del heapq
  del math
  return similar_values
\end{lstlisting}

@@

\hypertarget{alternative-filter-algorithm-implementation}{%
\subsection{Alternative Filter Algorithm
Implementation}\label{alternative-filter-algorithm-implementation}}

Another possibility here would be for the user to use a reference
measurement instead of a simulated ideal magnet as a reference. This can
come from a magnet selected as a reference magnet. As a result, the
filter algorithm returns the measurements that are most similar to the
selected reference magnet.The code snipped
\ref{lst:custom_find_similar_values_algorithm_refmagnet} shows the
modified filter algorithm code, with added
\passthrough{\lstinline!\_ref!} input parameter for the reference
measurement.

\begin{lstlisting}[language=Python, caption={Modified user implemented custom find algorithm using a reference magnet reading}, label=lst:custom_find_similar_values_algorithm_refmagnet]
@staticmethod
def FindSimilarValuesAlgorithmREF(_readings: [MRPReading.MRPReading], _ref: [MRPReading.MRPReading], IP_return_count: int = 4) -> [MRPReading.MRPReading]:
  # CALCULATE CoG VALUE OF REFERENCE MAGNET
  cog_ref = MRPAnalysis.MRPAnalysis.calculate_center_of_gravity(_ref[0])
  ref_value: float = math.sqrt(cog_ref[0]**2 + cog_ref[1]**2 cog_ref[2]**2)
  # PUSH READINGS TO HEAP
  for value in _readings:
      # USE DIFF AS PRIORITY VALUE IN MIN-HEAP
      cog = MRPAnalysis.MRPAnalysis.calculate_center_of_gravity(value)
      cog_value: float = math.sqrt(cog[0]**2 + cog[1]**2 cog[2]**2)
      heapq.heappush(heap, (abs(cog_value - ref_value), cog_value))
  # RETURN X BEST ITEMS FROM HEAP
  return [item[1] for item in heapq.nsmallest(IP_return_count, heap)]
\end{lstlisting}

@@

On the right-hand side
\ref{MRP_evaluation_result_after_execution_of_the _user_defined_pipeline,_using_find_similar_values_algorithm.png},
the measured values are plotted as a result of the filter algorithm. As
the \passthrough{\lstinline!IP\_return\_count!} parameter was set to
four, only the four most similar measurements were exported here. It can
be seen from the plotted \passthrough{\lstinline!CoG [uT]!} deviation
values, that these are closest to an ideal Magnet with a
\passthrough{\lstinline!CoG!} value of 0uT. This ideal value was
calculated with the function
\passthrough{\lstinline!MRP.MRPSimulation.generate\_simulated\_reading!},
with the same measurement parameters (magnet type, dimensions, sensor
distance) as they correspond to the mechanical structure of the used
hardware sensor \ref{d-fullsphere}.

The filter algorithm implemented by the user was thus successfully
executed using the user-programmable pipeline. The calculation result
was successfully verified using raw measurement data and the final
result of the algorithm.
